---
title: "Membrane permeabilization: Draft"
author: "Stelios Serghiou"
date: "2023-03-12"
output: html_document
---

# Setup

## Imports

```{r}
library(dplyr)
library(magrittr)
```


## Parameters

```{r}
# Source locations
src_dirname <- "../../data/tidy_data/membrane-permeabilization/"
src_basename <- "2023-03-11.csv"

# Destination locations
dst_dirname <- "../../outputs/draft/membrane-permeabilization/"
```


***

# Read

```{r}
# Read all csv files
membrane_ <- read_csv(file.path(src_dirname, src_basename))
```


***

# Conform

Create file.

```{r}
membrane <- membrane_
```


Glimpse.

```{r}
glimpse(membrane)
```


***

# Compute - Describe

Compute difference between channels.

```{r}
# Create channel columns and difference
wide <- 
  membrane %>% 
  pivot_wider(
    id_cols = condition,
    names_from = channel,
    names_glue = "channel_{channel}",
    values_from = mean_intensity
  ) %>% 
  mutate(diffs = channel_1 - channel_2)

# Compute mean in differences
mean_diff <- wide %>% pull(diffs) %>% mean

# Print mean
sprintf("Mean intensity difference in Channel 1 vs. 2 = %.1f units", mean_diff)
```


***

# Compute = Visualize

## Histograms

```{r}
# Plot
membrane_histogram <-
  membrane %>% 
  mutate(channel = paste("Channel", channel)) %>% 
  ggplot(aes(x = mean_intensity, fill = channel, color = channel)) +
  geom_histogram(alpha = 0.7) +
  facet_wrap(vars(condition)) +
  labs(x = "Mean intensity (units)", y = "Counts") +
  theme_minimal() +
  theme(
    axis.title.x = element_text(vjust = -1),
    axis.title.y = element_text(vjust = 3),
    legend.title = element_blank()
  )

# Save
ggsave(
  file.path(dst_dirname, "membrane_histogram.pdf"),
  p,
  height = 4,
  width = 6
)

# Print
membrane_histogram
```


## Images

I am choosing an image on the following criteria:
1. xxx
2. xxx
3. ...

On the basis of this criteria, I will be illustrating the following image:

```{r}
# Choose image
from_experiment <- "../../data/conformed_data/membrane-permeabilization/"
from_condition <- "detergent=digitonin_conc=0.02mmolar_minutes=1/"
from_basename <- "date=2022-03-19_488=poc5_594=cnb_01_01.tif"

# Copy paste to output directory
from <- file.path(from_experiment, from_condition, from_basename)
to <- file.path(dst_dirname, "example_image.tif")
file.copy(from, to)
```


***

# Compute - Analyze

This is where you can compute any p-values.


***

# Write

```{r}
```


***

# Documentation

## Session info

```{r}
print(sessionInfo(), locale = F)
```

## References

```{r}
(.packages()) %>% sort %>% lapply(citation) %>% lapply(c) %>% unique
```


